Clustering of Last.fm Music

### 2015-05-06 writeup/MSDgroupwriteup.tex

@@

\begin{figure}[ht]
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{h845BuzFO9CNgAAAABJRU5ErkJggg==.png}
\caption{default}
\label{fig:figure1}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{C9LAAAAABJRU5ErkJggg==.png}
\caption{default}
\label{fig:figure2}
\end{minipage}
\end{figure}

\subsection{Kmeans Clustering}
Next, we cluster each of the learned $u_i$ using k-means (describe more here later) so that the cluster centroids can be interpreted as listener/personality types.

>>>>

\section{Algorithms}

@@

%
%\begin{figure}[ht]
%\begin{minipage}[b]{0.45\linewidth}
%\centering
%\includegraphics[width=\textwidth]{h845BuzFO9CNgAAAABJRU5ErkJggg==.png}
%\caption{default}
%\label{fig:figure1}
%\end{minipage}
%\hspace{0.5cm}
%\begin{minipage}[b]{0.45\linewidth}
%\centering
%\includegraphics[width=\textwidth]{C9LAAAAABJRU5ErkJggg==.png}
%\caption{default}
%\label{fig:figure2}
%\end{minipage}
%\end{figure}

\subsection{Naked Kmeans }
Next, we cluster each of the learned $u_i$ using k-means (describe more here later) so that the cluster centroids can be interpreted as listener/personality types.

\subsection{Non-Negative Matrix Factorization}

\subsection{User based and Item based}

\subsection{Using Tags}

\section{Results}
